---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# rwrds

An R package for remotely obtaining and cleaning data from WRDS. Requires a valid WRDS account. 

## Highlights

- Simple-to-use functions for downloading data from the most commonly used WRDS databases. 

- Wrappers for submitting custom queries to the WRDS cloud. 

- Helper functions for data cleaning and linking to Compustat and CRSP. 

## Supported WRDS databases

In general, this package supports all WRDS databases. 

However, cleaning and linking functions are only available for a subset of the databases. 

Cleaning functions are available for the following databases: 

- Compustat

- CRSP

- Mergent

- TRACE

Linking functions are available for the following databases:

- Compustat and CRSP

- TRACE, Compustat, and CRSP

- Mergent, Compustat, and CRSP

## Usage

A detailed usage description can be found in the [vignette](https://github.com/davidsovich/rwrds/blob/master/vignettes/rwrds.pdf). 

Examples:

```{r, eval = FALSE}

# Connect to WRDS
wrds = wrds_connect(username = Sys.getenv("WRDS_NAME"), password = Sys.getenv("WRDS_PASS"))

#Download data from Compustat

   # Custom data series for CES state data
   ces_df = ces_download(bls_key = Sys.getenv("BLS_KEY"),
                      start_year = 2010,
                      end_year = 2015,
                      adjustment = "U",
                      industries = "05000000",
                      data_types = c("01", "03", "11"),
                      states = "1900000")
   
   # Pre-build CES data series for national employment
   ces_df = ces_employment(bls_key = Sys.getenv("BLS_KEY"),
                           start_year = 2010,
                           end_year = 2015)

#Download data from CRSP

   # Custom data series for JOLTS regional data
   jolts_df = jolts_download(bls_key = Sys.getenv("BLS_KEY"),
                             start_year = 2010,
                             end_year = 2015,
                             adjustment = "S",
                             industries = "000000",
                             data_types = "HI",
                             data_levels = "L",
                             regions = c("MW", "NE", "SO", "WE"))
   
   # Pre-built JOLTS data series
   jolts_df = jolts_hiring(bls_key = Sys.getenv("BLS_KEY"),
                           start_year = 2010,
                           end_year = 2015)
   
# Custom WRDS query

```

## Installation

The rwrds package is not available on CRAN. You can install the development version from Github:

```{r, eval = FALSE}
library("devtools")
devtools::install_github("davidsovich/rwrds")
```

## Contact

dsovich `AT` wustl.edu

## History

- April 5, 2019: Developmental release
